\documentclass[12pt]{article}
\usepackage{setspace}
\usepackage[letterpaper,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage[parfill]{parskip}

\title{BYLAWS
of the
ASSOCIATION FOR COMPUTING MACHINERY
of the
TRUMAN STATE UNIVERSITY STUDENT CHAPTER}
\begin{document}
	\maketitle
	
	\thispagestyle{empty}
	
		
\section{ARTICLE I – NAME}
\subsection{}	This organization shall be called the Association for Computing Machinery of the Truman State University Student Chapter. The Association is also referred to as Truman ACM.

\section{ARTICLE II – PURPOSE}
\subsection{}	The chapter is organized and will be operated exclusively for educational and scientific purposes and, in furtherance thereof, specific objectives are:
\subsubsection{}	To Promote an increased knowledge of the science, design, development, construction, languages, and applications of modern computing machinery;
\subsubsection{}	To promote a greater interest in computing machinery and its applications;
\subsubsection{}	To provide a means of communication between persons having interest in computing machinery
\subsubsection{}	To provide an environment which fosters computer science education.

\section{ARTICLE III – MEMBERSHIP}
	
\subsection{Categories for Membership}
	Active Members: shall be postsecondary students enrolled in Truman State University courses that accept the purpose of ACM, subscribe to its creed, demonstrate willingness to contribute to good school-community relations, and possess qualities for employment. Active members shall pay active member dues, shall join a committee.
\subsection{Eligibility for Active Membership}
\subsubsection{}	Pay active member dues
\subsubsection{}	Attend chapter meetings
\subsubsection{}	Attend committee meetings
\subsection{}	A full-time student of Truman State University who is an Active member is in good standing of Truman ACM, may become a voting member of this chapter.
\subsection{}	A member in good standing of Truman ACM who is not a full-time student at Truman State University, may become a voting member of this chapter, provided that the number of such non-student voting members shall not exceed one-half of the entire voting membership.
\subsection{}	A full or part-time student at Truman State University who is not a member in good standing of the Truman ACM, may upon request and payment of dues become a non-voting affiliate member of this chapter. No such person may be a non-voting affiliate member for more than one year.
\subsection{}	A member of the Truman State University community or the surrounding buisness community may, upon request and payment of a fee that is at least equal to the voting member dues, receive the chapter meeting notices and attend non-business meetings of this chapter.

\section{ARTICLE IV – OFFICERS}
\subsection{}	The officers of this chapter shall be President, Vice President, Secretary, Treasurer, and Web-master. Each officer must be a member in good standing of Truman ACM, a voting member of this chapter, and a full-time student at Truman State University.
\subsection{}	The officers shall be elected at the annual Election Meeting. They shall take office at the beginning of the proceeding semester and serve until their successors take office at the next academic or calendar year.
\subsection{}	The Secretary shall send two copies of the official notification to the President and Chapters Committees of changes in the elected officers to the Faculty Advisor. The Secretary shall similarly notify the Executive Director promptly of the final action of the proposed changes.
\subsection{}	Any member who has served in either of the offices of President or Vice President in each of two consecutive years, may not hold either office in the immediately following year.
\subsection{}	Vacancies in any office other than President caused by resignation, removal or disability shall be filled by majority vote of the members. If the office of President is so vacated, the Vice President shall immediately assume that office, and the Executive council shall fill the vacant office of Vice President. Vacancies should be filled by vote of the entire body.
\subsection{} officers can miss a maximum number of general meetings and/or executive meetings.
\subsubsection{} Number of general meetings that can be missed is determined by the executive board or two(2) if undetermined.
\subsubsection{} Number of executive meetings that can be missed is determined by the executive board or two(2) if undetermined.
\subsubsection{} Failure to comply attend meetings will lead to a removal vote by the remaining executive board. The faculty advisor will serve as a tie breaker in this situation.
\subsubsection{} If officer is removed, follow procedure in 4.5

\section{ARTICLE V – DUTIES OF THE OFFICERS}
\subsection{President}	The President shall preside at all meetings of this chapter and of its Executive Council. The President shall represent this chapter at all meetings with the ACM Regional Representative. The President shall also appoint all committees of this chapter and committee chairpersons, except the chairperson of the Program Committee.
\subsection{Vice President}	The Vice President shall assume the duties of President in the event of the President's absence. The Vice President shall assume those duties of the President that are so delegated by the President. The Vice President shall also be the President of the Program Committee.
\subsection{Secretary}	The Secretary shall keep minutes of all chapter meetings and Executive Council meetings. The secretary shall prepare the annual Election Meeting and prepare the report to the President and Chapters Committee after each meeting.
\subsection{Treasurer}	The Treasurer shall collect dues and maintains financial and membership records. The Treasurer shall make the annual reports of this chapter's finances required by the Treasurer of ACM.
\subsection{Web-master}
The Web-master shall maintain accuracy of the website information as soon as information is available. The web-master shall also maintain accuracy and communication on any active social media platform hosted by Truman ACM. The web-master is in charge of representing the club through advertising, such as but not limited to, web publications and paper publications. The web-master is also responsible for any communications delegated by the secretary and confirmed by the president. 

\section{ARTICLE VI – FACULTY ADVISOR}
\subsection{}	The Faculty Advisor shall be nominated by the Executive Council immediately following the annual Election Meeting and the nomination submitted to the Executive Director of the ACM via the President of the Truman State University ACM Chapter. The Faculty Advisor shall be the appointed chapter sponsor by the President to serve until a successor is appointed.
\subsection{}	The Faculty Advisor shall be generally responsible for the actives of this chapter.
\subsection{The Faculty Advisor shall}
\subsubsection{}	Help provide continuity from year to year as student leadership and personnel change;
\subsubsection{}	Promote good student-faculty relationships;
\subsubsection{}	Help maintain the standards of Truman State University in all activities of the organization;
\subsubsection{}	Promoting prompt payment of bills and collection of dues by the club
\subsubsection{}	Help oversee the settlement of all accounts in the event of dissouluton for this chapter
\subsubsection{}	Represent the student chapter interests to the faculty and administration of Truman State University.
\subsection{}	The Faculty Advisor shall be a member in good standing of the ACM.

\section{ARTICLE VII – EXECUTIVE COUNCIL}
\subsection{}	The Executive Council shall consist of the chapter officers, the immediate past President, and the Faculty Advisor. The Executive Council shall meet and nominate the Faculty Advisor immediately following the annual Election Meeting.
\subsection{}	Except as otherwise provided in these Bylaws, the Executive Council shall act for this chapter in all matters except election of officers at the annual Election Meeting and the amendment of these Bylaws. Minutes of all Executive Council meetings shall be available for inspection by any voting member of this chapter and shall be filed with the chapter records.
\subsection{}	Meetings the Executive Council shall be called by the President at their discretion or upon request of any member of the Executive Council.

\section{ARTICLE VIII – COMMITTEES}
\subsection{}	The Standing Committees shall be:
\subsubsection{}	The Program Committee, which shall plan and arrange meetings of the chapter in accordance with membership interests and the aims of this chapter as set forth in Article II; and shall prepare a calender of regularly scheduled meetings each year.
\subsubsection{}	The Publicity Committee, which shall maintain a mailing list, and publish and distribute all notices to the members of this chapter; and shall provide additional publicity of chapter activities as appropriate.
\subsection{}	Each standing committee shall consist of three voting members of this chapter; it may however have one or two additional members who are either voting or non-voting members of this chapter.
\subsection{}	All positions will be filled via Open Nominations by the body and approved of by a majority vote.
\subsection{}	In addition to the Standing Committees, Temporary Committees may be established by the chapter President.
\subsection{}	The President and the members of both Standing and Temporary Committees are appointed by the chapter President, except as otherwise provided in these Bylaws. All committee appointments shall terminate at the end of the annual Election Meeting.

\section{ARTICLE IX – MEETINGS}
\subsection{}	Meetings shall be held as planned by the Program Committee.
\subsubsection{}	This chapter may hold meetings in places that are open to all members of Truman ACM.
\subsection{}	The annual Election Meeting shall be held during the fall term of every year.
\subsubsection{}	Following the report of the Nominating Committee, additional nominations may be made from the floor by any voting member.
\subsubsection{}	After nominations are closed the voting members present shall vote.
\subsubsection{}	A Majority of votes cast for any office is necessary for election to that office.
\subsubsection{}	The Secretary shall present the annual chapter report.
\subsection{}	Written notices or emails shall be distributed to all members at least one week prior to any meeting.
\subsection{}	There shall be at least six meetings each year.
\subsection{}	A quorum of this chapter for the conduct of business shall consist of ten voting members or a majority of the members of this chapter, which ever is smaller.

\section{ARTICLE X – DISBURSEMENTS AND DUES}
\subsection{}	Disbursements from the Treasury for the chapter shall be made under authorization of the Executive Council and be included in the minutes of that meeting.
\subsection{}	Annual dues shall be established upon recommendation of the Executive Council and approved by a majority vote of the voting members present and voting at any chapter meeting, providing that the notice for the meeting included this as an item of business.

\section{ARTICLE XI – AMENDMENTS AND PROCEDURE}
\subsection{}	Amendments to these Bylaws shall be made in the following manner:
\subsubsection{}	The proposed amendment shall be read at a regularly announced chapter meeting.
\subsubsection{}	Three copies of the proposed amendment shall be sent to the Exectutive Director of the ACM, requesting the approval of the Chairperson of the ACM Student Membership and Chapters Committee and the Chairperson of the Truman ACM Constitution and Bylaws Committee.
\subsubsection{}	After approval has been received from the designated Truman ACM authority, the proposed amendment shall be distributed to the membership n writing with notice of a subsequent meeting at which the amendment will be considered.
\subsubsection{}	At the designated meeting the amendment shall be read again, discussed, and voting shall be required to adopt the amendment.
\subsection{}	The rules contained in Robert's Rules of Order Revised shall govern this chapter in all cases to which they are applicable, and in which they are not inconsistent with these Bylaws.
\subsection{}	Rulings on any point of procedure  not included in these Bylaws shall be made by the President with approval of the Faculty Advisor.

\section{ARTICLE XII – DISSOLUTION}
\subsection{}	In the event of revocation of the Truman ACM Charter, revocation of the Truman State University Charter or dissolution of this chapter, all assets of the chapter will be transferred to the Association for Computing Machinery.

\section{ARTICLE XIII – RISK MANAGEMENT}
\subsection{Risk Management Procedures}
\subsubsection{}	The Vice President is responsible for assessing and containing risk in addition to ensuring the chapters adherence to the below the guidelines.
\subsubsection{}	All members of this chapter of Truman ACM are required to adhere to the ACM Code of Ethics and Professional Conduct. Failure of a member to adhere to the Code of Ethics will result in the good standing of the member to be revoked until otherwise specified by a majority vote of the executive council in consultation with the faculty advisor.
\subsection{Anti-Hazing}
\subsubsection{}	Truman ACM fully understands and will abide by the anti-hazing policy as set forth in the Student Conduct Code of Truman State University 8.050.2. Expectations for Student Organization Conduct Section 14: Abusive affiliation
	



\end{document}
